---
title: "p8105_hw1_hc3653"
output: html_document
---

# Probem 1

```{r}
library(moderndive)
data("early_january_weather")
```

### The variables

This dataset contains variables of `r names(early_january_weather)`.

### The size

This dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

### The mean temperature

The mean temperature is `r round(mean(early_january_weather$temp),digit = 2)`

### PLot and descriptions

```{r}
library(ggplot2)

temp_time <-
  ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
       geom_point() +
       labs( title = "Temperature vs Time Hour",
             x = "Time_Hour",
             y = "Temperature")
print(temp_time)
```

From the plot, we can see that from early to mid-january, the temperature shows an increasing trend overall. However, the daily temperature fluctuates between day and night. When the temperature is higher, the humidity is also higher, therefore there is a positive relationship between temperature and humidity.

```{r}
ggsave(filename = "temp_vs_time.png",
       plot = temp_time )
```

# Problem 2

```{r}
library(tidyverse)
```

```{r}
p2_df = tibble(
  norm_samp = rnorm(10),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("apple","banana","peach","kiwi","mango",
               "strawberry","lemon","blueberry","grape","cherry"),
  vec_factor = factor(c("none", "a few", "none", "many", "many",
                        "a few", "none", "many", "a few", "a few"))
)
p2_df
```

```{r}
sapply(p2_df, mean)
```

As we can see from the result, it works for random sample and logical vector, but neither for character vector nor factor vector.

```{r}
mean(pull(p2_df, norm_samp))
mean(pull(p2_df, norm_samp_pos))
mean(pull(p2_df, vec_char))
mean(pull(p2_df, vec_factor))
```

```{r eval=FALSE}
as.numeric(p2_df$norm_samp_pos)
as.numeric(p2_df$vec_char)
as.numeric(p2_df$vec_factor)
```

For the logical vector, the function converts "TRUE" to 1 and "FALSE" to 0, since the logical values are internally stored as 0 and 1 in R. This explains why we can get the mean of logical vectors.

For the vector character, the result shows NA, becuase each character is unique and there are so many characters so that characters can't be converted to numerical numbers. So even by using the pull function, we still can't get the mean.

For the vector factor, they are stored as integers in R. For example, they can be converted to 1, 2 and etc according to levels assigned. But we need to apply the as.numeric function to accomplish this conversion, otherwise factors are not numerical numbers, thus we can't have the mean of it.
